\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\begin{document}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%   TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \colorbox{Sienna}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Michael}}}}} % First name
    \colorbox{Sienna}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sendker}}}}} % Last name

    \vspace{6pt}

    {\huge Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    % The first parameter is the FontAwesome icon name and the second is the
    % text Other icons can be found by referring to fontawesome5.pdf (supplied
    % with the template) and using the word after \fa in the command for the
    % icon you want
    \icon{MapMarker}{Tarpon Springs, FL}\\
    \href{tel:+1727-272-3915}{\icon{Phone}{+1 (727) 272-3915}}\\
    \href{mailto:m@stdwtr.io}{\icon{Envelope}{m@stdwtr.io}}\\
    \href{https://linkedin.com/in/michael-sendker}{\icon{Linkedin}{michael-sendker}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \href{https://standingwater.io}{\icon{Globe}{standingwater.io}}\\
    \href{https://github.com/malan88}{\icon{Github}{malan88}}\\
    \href{https://stackoverflow.com/story/malan88}{\icon{StackOverflow}{malan88}}\\
    \href{https://keybase.io/m88}{\icon{Keybase}{m88}}\\
\end{minipage}

% this vspace is largely useless and causes me to have trouble fitting everything
%\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%   INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who I Am}

I prefer Python, but I wear many hats. I have written code in C\#,
Python, vanilla JavaScript, and ReactJS. I have dabbled in C, Scheme, C++,
and Bash. I have built static sites in GatsbyJS, interfaces in WPF, and web
scrapers and bots in Python. I even built an arduino-based PID controller
for a popcorn popper to roast my own coffee. But by far most of my time has
been spent developing a single web technology, consisting of $\approx$
14,000 lines of code in Python, Flask, and SQLAlchemy, in the pursuit of my
obsession with literature:
{\href{https://github.com/malan88/icc}{\textcolor{Blue}{anno.wiki}}}.\\

All of this should demonstrate that I am a full time learner. I have spent
enough time learning new things that I have full confidence in my ability to
learn new things. But most of all, I am a thoughtful programmer. I think
twice about abstraction or hard coding, I think about tech debt and the way
users will interact with a feature. When I'm writing code in the present,
I'm thinking about the future.

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
    \entry
        {2021 -- Current}
        {\href{https://mbs-standoffs.com}{HtmMbs LLC}}
        {Software Developer}
        {
            \texttt{{\href{https://www.python.org/}{Python}}}\slashsep
            \texttt{{\href{https://flask.palletsprojects.com/en/1.1.x/}{Flask}}}\slashsep
            \texttt{{\href{https://www.sqlalchemy.org/}{SQLAlchemy}}}\slashsep
            \texttt{{\href{https://www.postgresql.org/}{PostgreSQL}}}\slashsep
            \texttt{{\href{https://jquery.com/}{jQuery}}}\slashsep
            \texttt{{\href{https://reactjs.org/}{ReactJS}}}\slashsep
            \texttt{{\href{https://www.odoo.com/}{Odoo}}}\\
            I built a sophisticated perpetual inventory system for the company
            to prioritize inventory checks by warehouse workers. Priority was
            calculated from around six different datapoints (e.g., cost of item,
            time since last counted, stock quantity, turnover, etc.) with a
            simple multinomial. The system provided resources for easily
            allocating and deallocating locations for inventories using the
            XMLRPC API for their highly customized and legacy Odoo system.\\

            I also deeply improved the Arduino code they used for led location
            indicators to help guide warehouse workers to inventories they were
            looking for, reducing the code from $\approx$450 lines to
            $\approx$50.\\

            In addition, I started a company wiki for general documentation, a
            GitHub organization for Version Control, a 1Password repository for
            security and helped them improve their backup systems.
        }
    \entry
        {2020 -- 2021}
        {Healthy Brands, LLC}
        {Contract Developer}
        {
            \texttt{{\href{https://www.python.org/}{Python}}}\slashsep
            \texttt{{\href{https://www.crummy.com/software/BeautifulSoup/bs4/doc/}{BeautifulSoup4}}}\slashsep
            \texttt{{\href{https://www.djangoproject.com/}{Django}}}\slashsep
            \texttt{{\href{https://www.sqlalchemy.org/}{SQLAlchemy}}}\slashsep
            \texttt{{\href{https://www.postgresql.org/}{PostgreSQL}}}\slashsep
            \texttt{{\href{https://archlinux.org/}{Arch Linux}}}\\
            I worked on several projects for this company.
            \begin{itemize}[leftmargin=*]
                \item I built and deployed a multithreaded scraper and alert system for notifying the company of BuyBox loss events on Amazon using a variety of data sources
                \item I launched, developed, and maintained {\href{https://ask.fiteyes.com}{ask.fiteyes.com}}, a Django-based question and answer forum built upon {\href{https://github.com/ialbert/biostar-central}{Biostar}}.  Contributed several bug fixes back upstream.
                \item I prepared and maintained several VPS servers, including one in Arch Linux
                \item I did general systems programming, including Systemd Units and Timers for varied infrastructure
            \end{itemize}
        }
    \entry
        {2020}
        {\href{https://euler-sci.com}{Euler Sciences LLC Website}}
        {Contract}
        {
            \texttt{{\href{https://www.adobe.com/products/photoshop.html}{Photoshop}}}\slashsep
            \texttt{{\href{https://www.gatsbyjs.org/}{GatsbyJS}}}\slashsep
            \texttt{{\href{https://reactjs.org/}{ReactJS}}}\slashsep
            \texttt{{\href{https://graphql.org/}{GraphQL}}}\\
            This was a very short contract on a hand shake agreement to design a
            contractor collective's main website. The company specializes in
            scientific and mathematical programming with occasional forays into
            more conventional programming paradigms.\\

            Because of the company's specialization in mathematics, I played up
            their mindset with a feature image of Leonhard Euler and their
            his namesake identity equation.
        }
    \entry
        {2020 -- 2021}
        {\href{https://euler-sci.com}{Laser System Interface}}
        {Contract}
        {
            \texttt{{\href{https://en.wikipedia.org/wiki/C_Sharp_(programming_language)}{C\#}}}\slashsep
            \texttt{{\href{https://en.wikipedia.org/wiki/Windows_Presentation_Foundation}{Windows Presentation Foundation}}}\slashsep
            \texttt{{\href{https://www.sqlite.org/index.html}{SQLite}}}\\
            Designing Euler's website demonstrated to them that I am a very
            capable interface developer, so they contracted me to help complete
            a tablet user interface for a contract they'd taken on for a laser
            system meant to treat skin conditions. It was a bit of a head first
            moment for me, as it was in a language I'd never written, C\#, a
            framework I'd never heard of, WPF, a programming domain I'd never
            worked in, tablet GUIs, and required the use of an IDE I'd never
            opened, Visual Studio. Within a matter of weeks I was writing View
            Models that have since gone into production around the world. I also
            helped design the database.
        }
    \entry
        {2019 -- Current}
        {{\href{https://github.com/Anno-Wiki}{Intertextual Canon Cloud 2}}}
        {Flask/React App}
        {
            \texttt{{\href{https://www.python.org/}{Python}}}\slashsep
            \texttt{{\href{https://flask.palletsprojects.com/en/1.1.x/}{Flask}}}\slashsep
            \texttt{{\href{https://www.sqlalchemy.org/}{SQLAlchemy}}}\slashsep
            \texttt{{\href{https://www.elastic.co/}{Elasticsearch}}}\slashsep
            \texttt{{\href{https://www.postgresql.org/}{PostgreSQL}}}\slashsep
            \texttt{{\href{https://www.docker.com/}{Docker}}}\slashsep
            \texttt{{\href{https://reactjs.org/}{ReactJS}}}\\
            This is the second iteration of the ICC (see below), with improved
            data architecture and a single-page application front end based in
            React. Using Elasticsearch to store texts and PostgreSQL to store
            annotations and general application data allows for faster
            incremental searching. I also wrote more sophisticated text
            processors for breaking text into 100k byte chunks and annotating
            stylistic elements, while stripping all styling from the raw text.\\
        }
    \entry
        {2017 -- 2020}
        {{\href{https://glendalepainting.com/}{Glendale Painting Corporation}}}
        {Office Manager, Technology Director}
        {
            \texttt{{\href{https://www.python.org/}{Python}}}\slashsep
            \texttt{{\href{https://www.gatsbyjs.org/}{GatsbyJS}}}\slashsep
            \texttt{{\href{https://reactjs.org/}{ReactJS}}}\slashsep
            \texttt{{\href{https://graphql.org/}{GraphQL}}}\slashsep
            \texttt{{\href{https://www.joomla.org/}{Joomla}}}\slashsep
            \texttt{{\href{https://quickbooks.intuit.com/}{Quickbooks}}}\slashsep
            \texttt{{\href{https://www.microsoft.com/en-us/microsoft-365/excel}{Excel}}}\\
            I did not anticipate a technology career, so my start was as an
            Office Manager working with Quickbooks and general company
            management. Soon after I began working on ICC I developed a love for
            technology and it began to permeate the company. I designed their
            current website based on a Joomla template, then I redesigned it
            using GatsbyJS. I also cleaned up a lot of the company's books using
            Python and macros, and helped build a maintainable static site
            for a yearly golf tournament the company uses for networking and
            marketing.
        }
    \entry
        {2017 -- 2019}
        {{\href{https://github.com/Anno-Wiki/icc}{Intertextual Canon Cloud (anno.wiki)}}}
        {Flask App}
        {
            \texttt{{\href{https://www.python.org/}{Python}}}\slashsep
            \texttt{{\href{https://flask.palletsprojects.com/en/1.1.x/}{Flask}}}\slashsep
            \texttt{{\href{https://www.sqlalchemy.org/}{SQLAlchemy}}}\slashsep
            \texttt{{\href{https://mariadb.org/}{MariaDB}}}\slashsep
            \texttt{{\href{https://www.elastic.co/}{Elasticsearch}}}\slashsep
            \texttt{{\href{https://docs.pytest.org/en/stable/}{pytest}}}\slashsep
            \texttt{{\href{https://www.heroku.com/}{Heroku}}}\\
            The ICC is a web application designed to allow for collaboratively
            building an exhaustive and definitive repository of annotated
            literature. I designed, developed, deployed, and continue to
            maintain the project solo, managing occasionally to rope in some
            programmer friends for help with various features. It consists of
            $\approx$ 14k lines of code and $\approx$ 100k lines of code churn.
            The backend uses Flask/SQLAlchemy. The frontend uses Jinja2, Sass,
            and VanillaJS. I also had to write several ETL data pipelines for
            processing {\href{https://gutenberg.org}{Project Gutenberg}} texts.
            It is deployed via Heroku. I learned the entire web application life
            cycle on this project, and it continues to teach me. It is currently
            maintained at {\href{https://anno.wiki}{https://anno.wiki}}.
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
    \entry
    {2008 -- 2010}
    {Philosophy and Classics}
    {Florida State University}
    {Focused on Ancient Philosophy, particularly Aristotle, Philosphy of
        Mind, and Symbolic Logic. Also studied Ancient Greek and Latin.
    President of Philosophy Club (2010)}
    \entry
    {2007 -- 2008}
    {Philosophy}
    {University of South Florida}
    {General introductory classes, Social Philosophy, Critical Thinking}
\end{entrylist}

%----------------------------------------------------------------------------------------
%   ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.2\textwidth}
    \vspace{-\baselineskip} % Required for vertically aligning minipages

    \cvsect{Languages}

    \textbf{English} — native,\\
    \textbf{French} — fluent,\\
    \textbf{Spanish} — rudimentary

\end{minipage}
\hfill
\begin{minipage}[t]{0.7\textwidth}
    \vspace{-\baselineskip} % Required for vertically aligning minipages

    \cvsect{Free Time}

    I am a lifelong learner, constantly finding new things to obsess over. In
    the last 3 years I've learned the intricacies of wine and cheese, learned to
    roast coffee and brew top-tier espresso, become a sophisticated mixologist,
    and learned to speak French.
\end{minipage}
%\hfill
%\begin{minipage}[t]{0.35\textwidth}
%    \vspace{-\baselineskip} % Required for vertically aligning minipages
%
%    \cvsect{Closing Argument}
%
%    I have had enough experience learning new things to have full confidence in
%    my ability to learn new things.
%\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
